Type cones of $\b{g}$-vector fans

### 2019-03-29 thirdPaper/draft/typeConeAssociahedra.tex

\begin{remark}
 Examples of categories satisfying the properties above are
 \begin{itemize}
  \item $2$-Calabi--Yau triangulated categories admitting a cluster-tilting object (see Section~\ref{sect::2CYTriangulated});
  \item $2$-Calabi--Yau Frobenius exact categories (see Section~\ref{sect::2CYexact});
  \item for any Artin algebra~$\Lambda$, the category~$K^{[-1,0]}(\proj \Lambda)$ of complexes of finitely generated projective~$\Lambda$-modules concentrated in degrees~$-1$ and~$0$, with morphisms considered up to homotopy (see Section~\ref{sect::Kbproj});
  \item more generally, extriangulated categories~$\cat$ constructed as follows: if~$\tc$ is a rigid subcategory of an extriangulated category~$\ec$, we let~$\cat$ be the full subcategory of~$\ec$ whose objects satisfy condition (3), equipped with the extriangulated structure obtained from that of~$\ec$ by considering those extriangles in~$\ec$ all whose terms belong to~$\cat$ and whose deflation is~$\tc$-epi (see Section~\ref{sect::Rigid}).
 \end{itemize}
\end{remark}

@@

Proposition~\ref{prop::KRextricat} below extends similar results from [REF]\yann{ref: BMR, KR ,KZ, IY...} (see also Proposition~\ref{prop::functor-F}) to the setting under consideration. We note that the proof requires minor modifications.

@@

The notion of index from \yann{ref RVdB, DK, P, also studied in ....} generalises to our current setting.

@@

%%%%
\subsection{Proof of Theorem~\ref{theorem::extricats}}
\label{sect::proofs extricats}

We let~$\cat$ and~$\tc$ be as in Setting~\ref{setting::extricat}.
We will make it explicit when more assumptions are needed.

>>>>

\begin{remark}
 Examples of categories satisfying the properties above are
 \begin{itemize}
  \item $2$-Calabi--Yau triangulated categories admitting a cluster-tilting object (see Section~\ref{sect::2CYTriangulated});
  \item $2$-Calabi--Yau Frobenius exact categories (see Section~\ref{sect::2CYexact});
  \item for any Artin algebra~$\Lambda$, the category~$K^{[-1,0]}(\proj \Lambda)$ of complexes of finitely generated projective~$\Lambda$-modules concentrated in degrees~$-1$ and~$0$, with morphisms considered up to homotopy (see Section~\ref{sect::Kbproj});
  \item more generally, extriangulated categories~$\cat$ constructed as follows: if~$\tc$ is a rigid subcategory of an extriangulated category~$\ec$, we let~$\cat$ be the full subcategory of~$\ec$ whose objects satisfy condition (3), equipped with the extriangulated structure obtained from that of~$\ec$ by considering those extriangles in~$\ec$ all whose terms belong to~$\cat$ and whose deflation is~$\tc$-epi (see Section~\ref{sect::prT}).
 \end{itemize}
\end{remark}

@@

Proposition~\ref{prop::KRextricat} below extends similar results from~\cite{BuanMarshReiten,KellerReiten,KoenigZhu,IyamaYoshino} (see also Proposition~\ref{prop::functor-F}) to the setting under consideration. We note that the proof requires minor modifications.

@@

The notion of index from~\cite{DehyKeller,Palu} \yann{ref RVdB ou BB ou ?, also studied in ....} generalises to our current setting.

@@

%%%%
\subsection{Proofs of preliminary results and of Theorem~\ref{theorem::extricats}}
\label{sect::proofs extricats}

We let~$\cat$ and~$\tc$ satisfy the assumptions (1), (2) and (3) of Setting~\ref{setting::extricat}.
We will make it explicit when more assumptions are needed.
